Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-13 paper/paper.tex
minor tweaks to abstract

\begin{abstract}
The outcome of viral infection is extremely heterogeneous at the cellular level, and many viruses trigger innate immunity in only a fraction of infected cells. 
Here we develop an approach to determine how the genetic variation inherent in viral populations contributes to this heterogeneity.
We simultaneously determine the cellular transcriptome and full sequences of all viral genes in hundreds of influenza-infected cells.
Infections that trigger immunity are associated with several features: absence of the gene encoding the virus's primary immune antagonist, internal deletions in viral polymerase genes, and point mutations in viral proteins involved in replication and nuclear export. 
However, immune activation remains stochastic in cells infected by viruses with these genetic lesions, and sometimes occurs even in cells infected with fully wildtype virions.
Overall, our work shows that viral genetic variation substantially contributes to but does not fully explain heterogeneity in infection outcome and immune activation.
\end{abstract}

>>>>

\begin{abstract}
The outcome of viral infection is extremely heterogeneous at the cellular level: infected cells vary widely in the amount of viral material they produce, and only sometimes activate innate immunity.  
Here we assess how the genetic variation inherent in viral populations contributes to this heterogeneity.
We determine the cellular transcriptome and full-length sequences of all viral genes in single influenza-infected cells.
Infections that trigger immunity at the single-cell level are associated with defects in the infecting viruses that include failure to express the primary immune antagonist, internal deletions in polymerase genes, and point mutations in proteins involved in replication and nuclear export. 
However, immune activation remains stochastic in cells infected by viruses with these genetic defects, and sometimes occurs even in cells infected with wildtype virus.
Our work shows that viral genetic variation substantially contributes to but does not fully explain heterogeneity in infection outcome and immune activation.
\end{abstract}
